Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-28 WSSSPE2_report/WSSSPE2_review.tex
Added authors affliations and emails.

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$, 
\\James Howison$^{(5)}$, Miguel de Val-Borro$^{(6)}$, Richard Littauer$^{(7)}$, more TBD %by contributions 
\\{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Gabrielle Allen$^{(11)}$,  \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$,  Miguel de Val-Borro$^{(10)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA}
%
\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA}
%
\thanks{{}$^{(4)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK}
%
\thanks{{}$^{(5)}$ TBD}
%
\thanks{{}$^{(6)}$ TBD}  
%
\thanks{{}$^{(7)}$ TBD}   
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA}

>>>>

\author{Daniel S. Katz$^{(1)}$, Sou-Cheng T. Choi$^{(2)}$, Nancy Wilkins-Diehr$^{(3)}$, Neil Chue Hong$^{(4)}$, 
\\James Howison$^{(5)}$, Miguel de Val-Borro$^{(6)}$, Richard Littauer$^{(7)}$, more TBD %by contributions 
\\{\scriptsize\today \quad  (Due:  $\backsim$ April 30)}} 
%\author{Gabrielle Allen$^{(11)}$,  \\
%Karen Cranston$^{(4)}$, Manish Parashar$^{(5)}$, David Proctor$^{(6)}$, \\
%Matthew Turk$^{(2)}$, Colin C. Venters$^{(7)}$,  Miguel de Val-Borro$^{(10)}$}
%
\thanks{{}$^{(1)}$ Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{dsk@uchicago.edu}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ University of California-San Diego, San Diego, CA, USA; \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(4)}$ Software Sustainability Institute, University of Edinburgh, Edinburgh, UK; \url{N.ChueHong@software.ac.uk}}
%
\thanks{{}$^{(5)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
%
\thanks{{}$^{(6)}$ Princeton University, Princeton, NJ, USA; \url{todo}}  
%
\thanks{{}$^{(7)}$ TODO; \url{todo}}   
%  
%\thanks{{}$^{(4)}$ National Evolutionary Synthesis Center, Durham, NC, USA}
%
%\thanks{{}$^{(5)}$ Rutgers Discovery Informatics Institute, Rutgers University, New Brunswick, NJ, USA}
%
%\thanks{{}$^{(6)}$ International Consortium of Research Staff Associations, Dublin, Ireland}
%
%\thanks{{}$^{(7)}$ University of Huddersfield, School of Computing and Engineering, Huddersfield, UK}
%
%\thanks{{}$^{(9)}$ Saarland University, Saarbr\"{u}cken, Germany}
%
%\thanks{{}$^{(10)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA}
%
%\thanks{{}$^{(11)}$ University of Illinois, Champaign, IL, USA}
